Working with Poisson regression

### 2021-09-21 text/21/direct-standardization.Rmd
Removed bad characters

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: "New"
date: "2020-09-20"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Direct standardization of mortality rates"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

### 2021-09-21 text/21/poisson-regression.Rmd
Removed bad characters

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: "New"
date: "2020-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---
